### 2019-07-08 1-Preamble/4-Acknowledgement/acknowledgement.tex
J'ai voulu ajouter Malone, Nadine et Bruno ❤

Of course on a more personal level, my thoughts are strongly dedicated to my family.
%
I first want to thank my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother Florian}, who has always been my main model and who has been of a constant support during all my life and in my studies.
His rigour, dedication and seriousness kept pushing me further, and I am immensely proud of him.
Some of our board game nights were brain teasers comparable with some maths problems solved for this thesis!
% and I was happy to help him for the organization of the \href{http://lettres.sorbonne-universite.fr/Kaamelott}{research colloque}\footnote{~Un livre a aussi été publié suite \href{http://lettres.sorbonne-universite.fr/Kaamelott}{au colloque}, \href{https://www.editions-vendemiaire.com/catalogue/a-paraitre/kaamelott-un-livre-d-histoire-florian-besson-et-justine-breton-dir/}{``Kaamelott, un livre d'histoire'', aux éditions Vandémiaire}.} on the \emph{Kaamelott} french TV show in February 2017, it was \href{https://www.fabula.org/actualites/kaamelott-ou-la-relecture-de-l-histoire_75490.php}{the funniest} and \href{https://www.vousnousils.fr/2017/03/22/kaamelott-un-tremplin-vers-lhistoire-et-la-litterature-601428}{most exciting} \href{https://lpcm.hypotheses.org/10718}{research event} I have been to in the last four years!
%
I also thank my younger brother Fabian, for being an inspiration for other (highly important) directions of my life. \emph{Ton courage et ta force m'inspirent quotidiennement, merci beaucoup !}
Very warm thanks then go to M. and my grand-parents, J. \& J.-M. and J., and to my uncle J. and aunt B.!
Finally, I thank sincerely my parents, C. and P., for being the best parents since the last $26$ years, and for their (vital) moral support.
\emph{Merci infiniment de nous avoir offert cette curiosité, merci d'être si gentils, et merci de votre soutien constant et de votre amour !}
% \\
% \indent

I would then like to thank my closest friends, sorted in chronological order of our first encounter in the \href{https://bulbapedia.bulbagarden.net/wiki/Tall_grass}{tall grass}\footnote{~Sorry if I forgot you, it's harder to keep track of wild encounters in the tall grass without a Pokédex!}: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia and Julia in Briançon, Mayotte and Pierre in Marseille, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément in Cachan, Jill-Jênn, Alain, Claire, Édouard, Loïc and Damien also in Cachan, Kumudham in India, Thibault, Sébastien, Sélim, Valentin again in Cachan, and Audrey, Rémi, Marine, Adrien, Bastien, Claire, Corentin and Lola in Rennes.
%  And due to space constraints, I had to choose quite arbitrarily whom to include\dots
% In the last four years, thank you so much my dear friends, for great moments and an even greater moral support, for the holidays in India, Switzerland, Hungary/Austria, Strasbourg, Greece, Saint-Malo, Normandy, Scotland, Marseille, Madrid, Brittany etc. I loved traveling with you and hope to continue!
\emph{J'ai une pensée particulière pour Hélène, merci pour ton énergie et ta détermination, notamment en 2018-19.}

Thanks to my wonderful colleagues during these three years: Rémi\textsuperscript{\tiny{\Coffeecup}}, Pascal\textsuperscript{\tiny{\Coffeecup}}, Yves, Amor, Carlos Faouzi, Jacques P., Jacques W., Ali C., Haïfa, Marwa, Navik, Quentin\textsuperscript{\tiny{\Coffeecup}}, Vincent\textsuperscript{\tiny{\Coffeecup}}, Rami\textsuperscript{\tiny{\Coffeecup}}, Pierre H., Muhammad, Cristo\textsuperscript{\tiny{\Coffeecup}}, Adrien\textsuperscript{\tiny{\Coffeecup}}, Esteban\textsuperscript{\tiny{\Coffeecup}}, Ali Z., Éloïse\textsuperscript{\tiny{\Coffeecup}}, Nabil\textsuperscript{\tiny{\Coffeecup}}, Bastien\textsuperscript{\tiny{\Coffeecup}}, Corentin\textsuperscript{\tiny{\Coffeecup}}, Julio, Georgios, Morgane\textsuperscript{\tiny{\Coffeecup}} in Rennes ; and Alessandro, Ronan, Julien P., Odalric-Ambrym, Philippe, Olivier, Florian, Xuedong, Guillaume, Benjamin, Julien S., Mathieu, Matteo, Mahsa, Nicolas, Sadegh, Édouard, Yannis and Omar in Lille.
I want to especially thank the ``coffee friends\textsuperscript{\tiny{\Coffeecup}}'' in Rennes, for our daily interesting discussions.
%  the best moments of our life at the office.
%
Thanks to everybody who played \emph{``futsal''} on Wednesday lunch,
% I still have to progress immensely,
% before I could pretend to be useful
but it's been a lot of fun to play with you guys!

@@

During my PhD, I was lucky to teach regularly in Mathematics and Computer Science.
I warmly thank David Pichardie for his trust and support, and also François Schwarzentruber, Nathalie Bertrand and David Cachera at ENS de Rennes, and Romaric Gaudel and his colleagues at ENSAI. Thanks to them, I loved to teach these $3 \times 64$ hours.
% since October $2016$.
% I am trully honored to join \emph{the Département d'Informatique} at ENS de Rennes in next September $2019$.
Thanks to my amazing students, I am proud of you and of our interesting exchanges.
%  and I feel lucky to be able to keep working alongside some of you.
I am thankful to Amélie Stainer and Gilbert Gabillard at Lycée Chateaubriand and Joliot-Curie for useful discussions.
\\
\indent
I am grateful to amazing professors who passed on their passion for mathematics and computer science to me.
A partial list includes Hubert P. in Briançon ($2006$-$09$), Yassine D. ($2009$-$10$) and Agnès B. ($2010$-$11$) in Lycée Thiers, Marseille.
Then at ENS de Cachan ($2011$-$16$), I especially think about Frédéric P., Alain T., Claudine P., Florian de V. and Nicolas V. in Maths, to Hubert C.-L., Jean G.-L., Sylvain S., Paul G., Serge H. in Computer Science, and to Carine S.-P., Delphine L. and Nicolas P.\textsuperscript{$\dagger$} for their support.
Thanks to Didier C. and Vijaysekhar C. in Hyderabad ($2014$-$15$), Michael U. and Julien F. in Lausanne ($2016$) for our collaborations.

@@

\emph{Je suis désolé si je vous ai oublié, merci de corriger} : Je remercie sincèrement ....................... pour .............
\emph{I am sorry I forgot you, please fix this mistake}: I warmly thank .................... for ..........

>>>>

Of course on a more personal level, my thoughts are strongly dedicated to my family.
%
I first want to thank my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother Florian}, who has always been my main model and who has been of a constant support during all my life and in my studies.
His rigour, dedication and seriousness kept pushing me further, and I am immensely proud of him.
Some of our board game nights were brain teasers comparable with some maths problems solved for this thesis!
% and I was happy to help him for the organization of the \href{http://lettres.sorbonne-universite.fr/Kaamelott}{research colloque}\footnote{~Un livre a aussi été publié suite \href{http://lettres.sorbonne-universite.fr/Kaamelott}{au colloque}, \href{https://www.editions-vendemiaire.com/catalogue/a-paraitre/kaamelott-un-livre-d-histoire-florian-besson-et-justine-breton-dir/}{``Kaamelott, un livre d'histoire'', aux éditions Vandémiaire}.} on the \emph{Kaamelott} french TV show in February 2017, it was \href{https://www.fabula.org/actualites/kaamelott-ou-la-relecture-de-l-histoire_75490.php}{the funniest} and \href{https://www.vousnousils.fr/2017/03/22/kaamelott-un-tremplin-vers-lhistoire-et-la-litterature-601428}{most exciting} \href{https://lpcm.hypotheses.org/10718}{research event} I have been to in the last four years!
%
I also thank my younger brother Fabian, for being an inspiration for other (highly important) directions of my life. \emph{Tes voyages, ton courage et ta force m'inspirent quotidiennement, merci beaucoup !}
I sincerely thank my parents C. \& P., for being the best parents since the last $26$ years, and for their (vital) moral support.
\emph{Merci infiniment de nous avoir offert cette curiosité, merci d'être si gentils, et merci de votre soutien constant et de votre amour !}
Very warm thanks then go to M., to my cousin L. and my grand-parents, J. \& J.-M. and J., to my uncle J. and aunt B.!
\emph{Merci enfin à M., N. \& B. pour votre accueil à La Gouesnière !}
% \\
% \indent

I would then like to thank my closest friends, sorted in chronological order of our first encounter in the \href{https://bulbapedia.bulbagarden.net/wiki/Tall_grass}{tall grass}\footnote{~Sorry if I forgot you, it's harder to keep track of wild encounters in the tall grass without a Pokédex!}: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia and Julia in Briançon, Mayotte and Pierre in Marseille, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément in Cachan, Jill-Jênn, Alain, Claire, Édouard, Loïc and Damien also in Cachan, Kumudham and Priscilla in India, Thibault, Sébastien, Sélim, Valentin again in Cachan, and Audrey, Rémi, Marine, Adrien, Bastien, Claire  and Lola in Rennes.
%  And due to space constraints, I had to choose quite arbitrarily whom to include\dots
% In the last four years, thank you so much my dear friends, for great moments and an even greater moral support, for the holidays in India, Switzerland, Hungary/Austria, Strasbourg, Greece, Saint-Malo, Normandy, Scotland, Marseille, Madrid, Brittany etc. I loved traveling with you and hope to continue!
\emph{J'ai une pensée particulière pour Hélène, merci pour ta foi, ton énergie et ta détermination, notamment en 2018-19.}

Thanks to my wonderful colleagues during these three years: Rémi\textsuperscript{\tiny{\Coffeecup}}, Pascal\textsuperscript{\tiny{\Coffeecup}}, Yves, Amor, Carlos Faouzi, Jacques P., Jacques W., Ali C., Haïfa, Marwa, Navik, Quentin\textsuperscript{\tiny{\Coffeecup}}, Vincent\textsuperscript{\tiny{\Coffeecup}}, Rami\textsuperscript{\tiny{\Coffeecup}}, Pierre H., Muhammad, Cristo\textsuperscript{\tiny{\Coffeecup}}, Adrien\textsuperscript{\tiny{\Coffeecup}}, Esteban\textsuperscript{\tiny{\Coffeecup}}, Ali Z., Éloïse\textsuperscript{\tiny{\Coffeecup}}, Nabil\textsuperscript{\tiny{\Coffeecup}}, Bastien\textsuperscript{\tiny{\Coffeecup}}, Corentin\textsuperscript{\tiny{\Coffeecup}}, Julio, Georgios, Morgane\textsuperscript{\tiny{\Coffeecup}} in Rennes ; and Alessandro, Ronan, Julien P., Odalric-Ambrym, Philippe, Olivier, Florian, Xuedong, Guillaume, Benjamin, Julien S., Mathieu, Matteo, Mahsa, Nicolas, Sadegh, Édouard, Yannis and Omar in Lille.
I want to especially thank the ``coffee friends\textsuperscript{\tiny{\Coffeecup}}'' in Rennes, for our daily interesting discussions.
%  the best moments of our life at the office.
%
Thanks to the \emph{``futsal''} players on Wednesday lunch,
% I still have to progress immensely,
% before I could pretend to be useful
I haven't been useful, but it's been a lot of fun to play with you guys!

@@

During my PhD, I was lucky to teach regularly in Mathematics and Computer Science.
I warmly thank David Pichardie for his trust and support, and also François Schwarzentruber, Nathalie Bertrand and David Cachera at ENS de Rennes, and Romaric Gaudel and his colleagues at ENSAI. Thanks to them, I loved to teach these $3 \times 64$ hours.
% since October $2016$.
% I am trully honored to join \emph{the Département d'Informatique} at ENS de Rennes in next September $2019$.
Thanks to my amazing students, I am proud of you and of our interesting exchanges.
%  and I feel lucky to be able to keep working alongside some of you.
I am thankful to Amélie Stainer and Gilbert Gabillard at Lycée Chateaubriand and Joliot-Curie for useful discussions.
\\
\indent
I am grateful to amazing professors who passed on their passion for mathematics and computer science to me.
A partial list includes Hubert P. in Briançon ($2006$-$09$), Yassine D. ($2009$-$10$) and Agnès B. ($2010$-$11$) in Lycée Thiers in Marseille.
Then at ENS de Cachan ($2011$-$16$), I especially think about Frédéric P., Alain T., Claudine P., Florian de V. and Nicolas V. in Maths, to Hubert C.-L., Jean G.-L., Sylvain S., Paul G., Serge H. in Computer Science, and to Carine S.-P., Delphine L. and Nicolas P.\textsuperscript{$\dagger$} for their support.
Thanks to Didier C. and Vijaysekhar C. in Hyderabad ($2014$-$15$), Michael U. and Julien F. in Lausanne ($2016$) for our collaborations.

@@

\emph{Je suis désolé si je vous ai oublié, merci de corriger} : Je remercie sincèrement ....................... pour .............
\emph{I am sorry I forgot you, please fix this mistake}: I warmly thank ..................... for ...............
